---
title: "Coho Salmon Project"
author: "Allen Li"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
---

# Reading in the data

```{r libraries and definitions}
# List required packages
packages <- c("readxl", "boot", "tinytex")

# Identify packages that are not installed yet
new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]

# Install missing packages
if (length(new_packages) > 0) {
  install.packages(new_packages)
}

# Load all packages
invisible(lapply(packages, library, character.only = TRUE))

# Ensure TinyTeX engine is installed for PDF compilation
if (!tinytex::is_tinytex()) {
  tinytex::install_tinytex()
}

# Change these if you want to run on your own machine
Saltwater <- read_excel("C:\\Users\\allen\\Downloads\\Coho data in excel (Raw).xlsx", sheet = 1)
Freshwater <- read_excel("C:\\Users\\allen\\Downloads\\Coho data in excel (Raw).xlsx", sheet = 2)

Freshwater$PCV1 <- as.numeric(Freshwater$PCV1)
Freshwater$PCV2 <- as.numeric(Freshwater$PCV2)
Saltwater$PCV2 <- as.numeric(Saltwater$PCV2)

Saltwater$PCV_Avg <- rowMeans(Saltwater[, c("PCV1", "PCV2")], na.rm = TRUE)
Freshwater$PCV_Avg <- rowMeans(Freshwater[, c("PCV1", "PCV2")], na.rm = TRUE)

vars <- c(
  "Heart Rate (/min)",
  "Rectal Temp \"C\"",
  "Right IR (F)",
  "Left IR (F)",
  "Dorsal IR (F)",
  "Weight (kg)",
  "Length (cm)",
  "Lac",
  "HemoCue (g/dl)", 
  "PCV1", 
  "PCV2",
  "TS",
  "Na (mmol/L)",
  "K (mmol/L)",
  "Cl (mmol/L)",
  "iCa (mmol/L)",
  "TCO2 (mmol/L)",
  "Glu (mg/dL)",
  "Hct (%PCV)",
  "Hb* (g/dL)",
  "BUN (mg/dL)", 
  "Crea (mg/dL)",
  "WBC estimate K/μl",
  "Absolute Neutrophils K/μl",
  "Absolute immature neutrophils K/μl",
  "Absolute Lymphocytes K/μl",
  "Absolute Monocytes K/μl",
  "Absolute Eosinophils K/μl",
  "Absolute Basophils K/μl",
  "#immature RBC/100 mature RBC",
  "PCV_Avg"
)

# Forcing the columns to be numeric - normally what happens is that when you have NA in your dataset it changes the column to be characters
Saltwater[vars] <- lapply(Saltwater[vars], function(x) {
  
  x <- trimws(x)                 # remove extra spaces
  x[x %in% c("NA", "***", "")] <- NA
  
  as.numeric(x)
  
})

Freshwater[vars] <- lapply(Freshwater[vars], function(x) {
  
  x <- trimws(x)                 # remove extra spaces
  x[x %in% c("NA", "***", "")] <- NA
  
  as.numeric(x)
  
})

```

# Analyzing Saltwater Salmon

Pages 8 - 10

1\. Determine if data is Gaussian/Nongaussian based on Shapiro Wilk\
2. Remove outliers\
3. Calculate reference Intervals

If sample size below 20: Do not need to calculate RI.\
NEED:\
- Histogram of Data (Including outliers)\
- Mean (if Gaussian) or Median (if not Gaussian)\
- Minimum and Maximum Values

## Gaussian? (Shapiro Wilk)

```{r gaussian or not saltwater}
shapiro_p <- numeric(length(vars))
n_values <- numeric(length(vars))

names(shapiro_p) <- vars
names(n_values) <- vars

shapiro_p <- numeric(length(vars))
shapiro_W <- numeric(length(vars))
n_values <- numeric(length(vars))

names(shapiro_p) <- vars
names(shapiro_W) <- vars
names(n_values) <- vars

for (v in vars) {
  
  x <- na.omit(Saltwater[[v]])
  n_values[v] <- length(x)
  
  if (length(x) >= 3 && length(unique(x)) > 1) {
    
    test <- shapiro.test(x)
    shapiro_p[v] <- test$p.value
    shapiro_W[v] <- test$statistic
    
  } else {
    
    shapiro_p[v] <- NA
    shapiro_W[v] <- NA
    
  }
}

Saltwater_Normality <- data.frame(
  Variable = vars,
  N = n_values,
  Shapiro_p_value = shapiro_p,
  Normal = ifelse(shapiro_p > 0.05, "Yes", "No")
)

Saltwater_Normality
```

## Gaussian Data - Removing outliers

Page 8 of the Guidelines for RI from ASVCP (Horn's Algorithm)

Page 9: Eliminate outliers, retest, eliminate again.

Directly from the guidelines: ***NOTE: The RI study summary document should reflect the number of outliers eliminated, the method used to identify them and the final number (n) from which RI are determined.***

```{r saltwater gauss remove outlier}
normal_vars <- Saltwater_Normality$Variable[
  !is.na(Saltwater_Normality$Normal) &
  Saltwater_Normality$Normal == "Yes"
]

Saltwater_NoOutliers <- Saltwater

outliers_removed_salt <- numeric(length(normal_vars))
final_nonNA_salt <- numeric(length(normal_vars))

names(outliers_removed_salt) <- normal_vars
names(final_nonNA_salt) <- normal_vars

for (v in normal_vars) {
  
  removed_total <- 0
  
  repeat {
    
    x <- Saltwater_NoOutliers[[v]]
    x_noNA <- na.omit(x)
    
    Q1 <- quantile(x_noNA, 0.25)
    Q3 <- quantile(x_noNA, 0.75)
    IQR_value <- IQR(x_noNA)
    
    lower <- Q1 - 1.5 * IQR_value
    upper <- Q3 + 1.5 * IQR_value
    
    outliers <- which(x < lower | x > upper)
    
    if (length(outliers) == 0) break
    
    removed_total <- removed_total + length(outliers)
    
    Saltwater_NoOutliers[[v]][outliers] <- NA
    
  }
  
  outliers_removed_salt[v] <- removed_total
  final_nonNA_salt[v] <- sum(!is.na(Saltwater_NoOutliers[[v]]))
}

Saltwater_results <- data.frame(
  Variable = normal_vars,
  Outliers_Removed = outliers_removed_salt,
  Final_NonNA = final_nonNA_salt
)

rownames(Saltwater_results) <- NULL
Saltwater_results
```

## Mean +- 1.96 \* SD for 20 $\leq$ n $<$ 40 and Gaussian

```{r reference intervals for salt gaussian}
# qnorm(0.95) Number to multiply the SD by for Gaussian Data
# Uncomment this install.packages below if you need the package to run
# install.packages("boot")
library(boot)
set.seed(352026)

# Function used by bootstrap
bootstrap_RI <- function(data, indices) {
  
  d <- data[indices]
  
  mean_d <- mean(d)
  sd_d <- sd(d)
  
  c(
    mean_d - 1.96 * sd_d,
    mean_d + 1.96 * sd_d
  )
}

vars_param <- Saltwater_results$Variable[
  Saltwater_results$Final_NonNA >= 20 &
  Saltwater_results$Final_NonNA < 40
]

param_results <- data.frame()

for (v in vars_param) {
  
  x <- na.omit(Saltwater_NoOutliers[[v]])
  
  n <- length(x)
  mean_x <- mean(x)
  sd_x <- sd(x)
  min_x <- min(x)
  max_x <- max(x)
  
  RI_lower <- mean_x - 1.96 * sd_x
  RI_upper <- mean_x + 1.96 * sd_x
  
  # Bootstrap CI
  results <- boot(x, statistic = bootstrap_RI, R = 10000)
  
  lower_ci <- boot.ci(results, conf = 0.90, type = "perc", index = 1)$percent[4:5]
  upper_ci <- boot.ci(results, conf = 0.90, type = "perc", index = 2)$percent[4:5]
  
  param_results <- rbind(
    param_results,
    data.frame(
      Variable = v,
      N = n,
      OutliersRemoved = Saltwater_results$Outliers_Removed[Saltwater_results$Variable == v],
      Minimum = min_x,
      Maximum = max_x,
      Mean = mean_x,
      SD = sd_x,
      RI_lower = RI_lower,
      RI_upper = RI_upper,
      CI90_lower_L = lower_ci[1],
      CI90_lower_U = lower_ci[2],
      CI90_upper_L = upper_ci[1],
      CI90_upper_U = upper_ci[2]
    )
  )
}

rownames(param_results) <- NULL
param_results
```

## Finishing off the Gaussian data (n below 20)

Need:\
- Histogram of data\
- Mean\
- Minimum and Maximum values

```{r saltwater gaussian n below 20}
vars_hist <- Saltwater_results$Variable[
  Saltwater_results$Final_NonNA < 20
]

results_summary_salt <- data.frame()

for (v in vars_hist) {
  
  x <- na.omit(Saltwater_NoOutliers[[v]])
  
  hist(x,
       main = paste("Histogram of", v, "(Saltwater - Gaussian)"),
       xlab = v,
       col = "lightblue",
       border = "black")
  cat("\n\\newpage\n")
  
  n <- length(x)
  mean_val <- mean(x)
  min_val <- min(x)
  max_val <- max(x)
  
  values_sorted <- paste(sort(x), collapse = ", ")
  
  results_summary_salt <- rbind(
    results_summary_salt,
    data.frame(
      Variable = v,
      N = n,
      OutliersRemoved = Saltwater_results$Outliers_Removed[Saltwater_results$Variable == v],
      Mean = mean_val,
      Minimum = min_val,
      Maximum = max_val,
      Values = values_sorted
    )
  )
}

results_summary_salt
```

## Saltwater not Gaussian 20 $\leq$ n $<$ 40

```{r saltwater not gaussian n between 20 and 40}
library(boot)
set.seed(352026)

bootstrap_RI_np <- function(data, indices) {
  
  d <- data[indices]
  
  c(
    quantile(d, 0.025),
    quantile(d, 0.975)
  )
}

nonnormal_vars <- Saltwater_Normality$Variable[
  !is.na(Saltwater_Normality$Normal) &
  Saltwater_Normality$Normal == "No"
]

vars_np <- nonnormal_vars[
  sapply(nonnormal_vars, function(v)
    sum(!is.na(Saltwater_NoOutliers[[v]])) >= 20 &
    sum(!is.na(Saltwater_NoOutliers[[v]])) < 40
  )
]

nonnormal_results <- data.frame()

for (v in vars_np) {
  
  x <- na.omit(Saltwater_NoOutliers[[v]])
  
  n <- length(x)
  min_x <- min(x)
  max_x <- max(x)
  med_x <- median(x)
  
  RI_lower <- quantile(x, 0.025)
  RI_upper <- quantile(x, 0.975)
  
  # Bootstrap
  results <- boot(x, statistic = bootstrap_RI_np, R = 10000)
  
  lower_ci <- boot.ci(results, conf = 0.90, type = "perc", index = 1)$percent[4:5]
  upper_ci <- boot.ci(results, conf = 0.90, type = "perc", index = 2)$percent[4:5]
  
  nonnormal_results <- rbind(
    nonnormal_results,
    data.frame(
      Variable = v,
      N = n,
      Minimum = min_x,
      Maximum = max_x,
      Median = med_x,
      RI_lower = RI_lower,
      RI_upper = RI_upper,
      CI90_lower_L = lower_ci[1],
      CI90_lower_U = lower_ci[2],
      CI90_upper_L = upper_ci[1],
      CI90_upper_U = upper_ci[2]
    )
  )
}

rownames(nonnormal_results) <- NULL
nonnormal_results
```

## Saltwater not Gaussian (n below 20)

```{r saltwater not gaussian n below 20}
nonnormal_vars <- Saltwater_Normality$Variable[
  !is.na(Saltwater_Normality$Normal) &
  Saltwater_Normality$Normal == "No"
]

vars_small_np <- nonnormal_vars[
  sapply(nonnormal_vars, function(v)
    sum(!is.na(Saltwater[[v]])) < 20
  )
]

results_summary_small_np <- data.frame()

for (v in vars_small_np) {
  
  x <- na.omit(Saltwater[[v]])
  

hist(x,
     main = paste("Histogram of", v, "\n(Saltwater - Not Gaussian)"),
     xlab = v,
     col = "lightblue",
     border = "black")

  cat("\n\\newpage\n")
  
  n <- length(x)
  median_val <- median(x)
  min_val <- min(x)
  max_val <- max(x)
  
  values_sorted <- paste(sort(x), collapse = ", ")
  
  results_summary_small_np <- rbind(
    results_summary_small_np,
    data.frame(
      Variable = v,
      N = n,
      Median = median_val,
      Minimum = min_val,
      Maximum = max_val,
      Values = values_sorted
    )
  )
}

results_summary_small_np
```

# Saltwater Results

```{r results for saltwater}
param_results
results_summary_salt
nonnormal_results
results_summary_small_np

# No category
Saltwater_Normality$Variable[is.na(Saltwater_Normality$Normal)]
```

# Analyzing Freshwater Salmon

## Gaussian? (Shapiro - Wilk)

```{r freshwater gaussian}
shapiro_p <- numeric(length(vars))
shapiro_W <- numeric(length(vars))
n_values <- numeric(length(vars))

names(shapiro_p) <- vars
names(shapiro_W) <- vars
names(n_values) <- vars

for (v in vars) {
  
  x <- na.omit(Freshwater[[v]])
  n_values[v] <- length(x)
  
  if (length(x) >= 3 && length(unique(x)) > 1) {
    
    test <- shapiro.test(x)
    shapiro_p[v] <- test$p.value
    shapiro_W[v] <- test$statistic
    
  } else {
    
    shapiro_p[v] <- NA
    shapiro_W[v] <- NA
    
  }
}

Freshwater_Normality <- data.frame(
  Variable = vars,
  N = n_values,
  Shapiro_p_value = shapiro_p,
  Normal = ifelse(shapiro_p > 0.05, "Yes", "No")
)

Freshwater_Normality
```

## Gaussian Data - Removing outliers

```{r freshwater gauss remove outliers}
normal_vars_fw <- Freshwater_Normality$Variable[
  !is.na(Freshwater_Normality$Normal) &
  Freshwater_Normality$Normal == "Yes"
]

Freshwater_NoOutliers <- Freshwater

outliers_removed_fw <- numeric(length(normal_vars_fw))
final_nonNA_fw <- numeric(length(normal_vars_fw))

names(outliers_removed_fw) <- normal_vars_fw
names(final_nonNA_fw) <- normal_vars_fw

for (v in normal_vars_fw) {
  
  removed_total <- 0
  
  repeat {
    
    x <- Freshwater_NoOutliers[[v]]
    x_noNA <- na.omit(x)
    
    Q1 <- quantile(x_noNA, 0.25)
    Q3 <- quantile(x_noNA, 0.75)
    IQR_value <- IQR(x_noNA)
    
    lower <- Q1 - 1.5 * IQR_value
    upper <- Q3 + 1.5 * IQR_value
    
    outliers <- which(x < lower | x > upper)
    
    if (length(outliers) == 0) break
    
    removed_total <- removed_total + length(outliers)
    
    Freshwater_NoOutliers[[v]][outliers] <- NA
    
  }
  
  outliers_removed_fw[v] <- removed_total
  final_nonNA_fw[v] <- sum(!is.na(Freshwater_NoOutliers[[v]]))
}

Freshwater_results <- data.frame(
  Variable = normal_vars_fw,
  Outliers_Removed = outliers_removed_fw,
  Final_NonNA = final_nonNA_fw
)

rownames(Freshwater_results) <- NULL
Freshwater_results
```

## Mean +- 1.96 \* SD for 20 $\leq$ n $<$ 40 and Gaussian

```{r reference intervals for freshwater gaussian}
library(boot)
set.seed(352026)

bootstrap_RI <- function(data, indices) {
  
  d <- data[indices]
  
  mean_d <- mean(d)
  sd_d <- sd(d)
  
  c(
    mean_d - 1.96 * sd_d,
    mean_d + 1.96 * sd_d
  )
}

vars_param_fw <- Freshwater_results$Variable[
  Freshwater_results$Final_NonNA >= 20 &
  Freshwater_results$Final_NonNA < 40
]

param_results_fw <- data.frame()

for (v in vars_param_fw) {
  
  x <- na.omit(Freshwater_NoOutliers[[v]])
  
  n <- length(x)
  mean_x <- mean(x)
  sd_x <- sd(x)
  min_x <- min(x)
  max_x <- max(x)
  
  RI_lower <- mean_x - 1.96 * sd_x
  RI_upper <- mean_x + 1.96 * sd_x
  
  results <- boot(x, statistic = bootstrap_RI, R = 10000)
  
  lower_ci <- boot.ci(results, conf = 0.90, type = "perc", index = 1)$percent[4:5]
  upper_ci <- boot.ci(results, conf = 0.90, type = "perc", index = 2)$percent[4:5]
  
  param_results_fw <- rbind(
    param_results_fw,
    data.frame(
      Variable = v,
      N = n,
      OutliersRemoved = Freshwater_results$Outliers_Removed[Freshwater_results$Variable == v], 
      Minimum = min_x,
      Maximum = max_x,
      Mean = mean_x,
      SD = sd_x,
      RI_lower = RI_lower,
      RI_upper = RI_upper,
      CI90_lower_L = lower_ci[1],
      CI90_lower_U = lower_ci[2],
      CI90_upper_L = upper_ci[1],
      CI90_upper_U = upper_ci[2]
    )
  )
}

rownames(param_results_fw) <- NULL
param_results_fw
```

## Finishing off the Gaussian data (n below 20)

```{r freshwater gaussian n below 20}
vars_hist_fw <- Freshwater_results$Variable[
  Freshwater_results$Final_NonNA < 20
]

results_summary_fw <- data.frame()

for (v in vars_hist_fw) {
  
  x <- na.omit(Freshwater_NoOutliers[[v]])
  
  hist(x,
       main = paste("Histogram of", v, "(Freshwater - Gaussian)"),
       xlab = v,
       col = "lightblue",
       border = "black")
  cat("\n\\newpage\n")
  
  n <- length(x)
  mean_val <- mean(x)
  min_val <- min(x)
  max_val <- max(x)
  
  values_sorted <- paste(sort(x), collapse = ", ")
  
  results_summary_fw <- rbind(
    results_summary_fw,
    data.frame(
      Variable = v,
      N = n,
      OutliersRemoved = Freshwater_results$Outliers_Removed[Freshwater_results$Variable == v],
      Mean = mean_val,
      Minimum = min_val,
      Maximum = max_val,
      Values = values_sorted
    )
  )
}

results_summary_fw
```

## Freshwater not Gaussian 20 \< n \< 40

```{r freshwater not gaussian n between 20 and 40}
bootstrap_RI_np <- function(data, indices) {
  
  d <- data[indices]
  
  c(
    quantile(d, 0.025),
    quantile(d, 0.975)
  )
}

nonnormal_vars_fw <- Freshwater_Normality$Variable[
  !is.na(Freshwater_Normality$Normal) &
  Freshwater_Normality$Normal == "No"
]

vars_np_fw <- nonnormal_vars_fw[
  sapply(nonnormal_vars_fw, function(v)
    sum(!is.na(Freshwater_NoOutliers[[v]])) >= 20 &
    sum(!is.na(Freshwater_NoOutliers[[v]])) < 40
  )
]

nonnormal_results_fw <- data.frame()

for (v in vars_np_fw) {
  
  x <- na.omit(Freshwater_NoOutliers[[v]])
  
  n <- length(x)
  min_x <- min(x)
  max_x <- max(x)
  med_x <- median(x)
  
  RI_lower <- quantile(x, 0.025)
  RI_upper <- quantile(x, 0.975)
  
  results <- boot(x, statistic = bootstrap_RI_np, R = 10000)
  
  lower_ci <- boot.ci(results, conf = 0.90, type = "perc", index = 1)$percent[4:5]
  upper_ci <- boot.ci(results, conf = 0.90, type = "perc", index = 2)$percent[4:5]
  
  nonnormal_results_fw <- rbind(
    nonnormal_results_fw,
    data.frame(
      Variable = v,
      N = n,
      Minimum = min_x,
      Maximum = max_x,
      Median = med_x,
      RI_lower = RI_lower,
      RI_upper = RI_upper,
      CI90_lower_L = lower_ci[1],
      CI90_lower_U = lower_ci[2],
      CI90_upper_L = upper_ci[1],
      CI90_upper_U = upper_ci[2]
    )
  )
}

rownames(nonnormal_results_fw) <- NULL
nonnormal_results_fw
```

## Freshwater not Gaussian (n below 20)

```{r freshwater not gaussian n below 20}
vars_small_np_fw <- nonnormal_vars_fw[
  sapply(nonnormal_vars_fw, function(v)
    sum(!is.na(Freshwater[[v]])) < 20
  )
]

results_summary_small_np_fw <- data.frame()

for (v in vars_small_np_fw) {
  
  x <- na.omit(Freshwater[[v]])
  
  hist(x,
       main = paste("Histogram of", v, "(Freshwater - Not Gaussian)"),
       xlab = v,
       col = "lightblue",
       border = "black")
  
  cat("\n\\newpage\n")
  
  n <- length(x)
  median_val <- median(x)
  min_val <- min(x)
  max_val <- max(x)
  
  values_sorted <- paste(sort(x), collapse = ", ")
  
  results_summary_small_np_fw <- rbind(
    results_summary_small_np_fw,
    data.frame(
      Variable = v,
      N = n,
      Median = median_val,
      Minimum = min_val,
      Maximum = max_val,
      Values = values_sorted
    )
  )
}

results_summary_small_np_fw
```

# Freshwater Results

```{r results for freshwater}
param_results_fw
results_summary_fw
nonnormal_results_fw
results_summary_small_np_fw

Freshwater_Normality$Variable[is.na(Freshwater_Normality$Normal)]
```

# T-Tests and BH Correction

```{r t tests and benjamini hochberg correction}
p_values <- numeric(length(vars))
mean_salt <- numeric(length(vars))
mean_fresh <- numeric(length(vars))
difference <- numeric(length(vars))
se_diff <- numeric(length(vars))
t_ratio <- numeric(length(vars))
df_val <- numeric(length(vars))

names(p_values) <- vars
names(mean_salt) <- vars
names(mean_fresh) <- vars
names(difference) <- vars
names(se_diff) <- vars
names(t_ratio) <- vars
names(df_val) <- vars

for (v in vars) {

  x <- na.omit(Saltwater[[v]])
  y <- na.omit(Freshwater[[v]])

  if (length(x) > 2 && length(y) > 2) {

    test <- t.test(x, y)

    p_values[v] <- test$p.value
    mean_salt[v] <- mean(x)
    mean_fresh[v] <- mean(y)
    difference[v] <- mean(x) - mean(y)
    se_diff[v] <- test$stderr
    t_ratio[v] <- test$statistic
    df_val[v] <- test$parameter

  } else {

    p_values[v] <- NA
    mean_salt[v] <- NA
    mean_fresh[v] <- NA
    difference[v] <- NA
    se_diff[v] <- NA
    t_ratio[v] <- NA
    df_val[v] <- NA

  }
}

q_values <- p.adjust(p_values, method = "BH")

comparison_results <- data.frame(
  Variable = vars,
  Mean_Saltwater = round(mean_salt, 3),
  Mean_Freshwater = round(mean_fresh, 3),
  Difference = round(difference, 3),
  SE_Difference = round(se_diff, 3),
  T_ratio = round(t_ratio, 3),
  DF = round(df_val, 2),
  P_value = signif(p_values, 3),
  Q_value = signif(q_values, 3),
  Significant = ifelse(q_values < 0.05, "Yes", "No")
)

comparison_results
```

# Exporting Results to CSVs

```{r exporting results to csv files}
# Change this working directory if you want to run on your own machine
setwd("C:\\Users\\allen\\OneDrive\\Desktop\\Coho Salmon Project")
getwd()

# Salt
write.csv(param_results, "Saltwater_GaussianResults.csv", row.names = FALSE)
write.csv(results_summary_salt, "Saltwater_SmallGaussianSummary.csv", row.names = FALSE)
write.csv(nonnormal_results, "Saltwater_NonGaussianResults.csv", row.names = FALSE)
write.csv(results_summary_small_np, "Saltwater_SmallNonGaussian.csv", row.names = FALSE)
write.csv(
  data.frame(Variable = Saltwater_Normality$Variable[is.na(Saltwater_Normality$Normal)]),
  "Saltwater_NA.csv",
  row.names = FALSE
)

# Fresh
write.csv(param_results_fw, "Freshwater_GaussianResults.csv", row.names = FALSE)
write.csv(results_summary_fw, "Freshwater_SmallGaussianSummary.csv", row.names = FALSE)
write.csv(nonnormal_results_fw, "Freshwater_NonGaussianResults.csv", row.names = FALSE)
write.csv(results_summary_small_np_fw, "Freshwater_SmallNonGaussian.csv", row.names = FALSE)
write.csv(
  data.frame(Variable = Freshwater_Normality$Variable[is.na(Freshwater_Normality$Normal)]),
  "Freshwater_NA.csv",
  row.names = FALSE
)

# T-Test and BH Correction
write.csv(comparison_results, "Comparison_Results.csv", row.names = FALSE)
```
